Results

### 2023-03-28 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
table 1 is the anti hero

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, \emph{Corrugator} and \emph{Levator} activity of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 0.21\)), \emph{Corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 6.16 \times 10^{7}\)), and \emph{Levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 3.22 \times 10^{17}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc tests, please see tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in the \protect\hyperlink{SupplementEffectER}{supplementary material}.
{[}INSERT TABLE 1 HERE{]}

\begin{lltable}

\begin{longtable}{llllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:TabDescr}$M \pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.}\\
\toprule
 & \multicolumn{1}{c}{Subjective Arousal} & \multicolumn{1}{c}{Subjective Effort} & \multicolumn{1}{c}{Subjective Utility} & \multicolumn{1}{c}{Corrugator activity (in mV)} & \multicolumn{1}{c}{Levator activity (in mV)}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:TabDescr} continued}}\\
\toprule
 & \multicolumn{1}{c}{Subjective Arousal} & \multicolumn{1}{c}{Subjective Effort} & \multicolumn{1}{c}{Subjective Utility} & \multicolumn{1}{c}{Corrugator activity (in mV)} & \multicolumn{1}{c}{Levator activity (in mV)}\\
\midrule
\endhead
$View_{neu}$ & 26.6 ± 39.1 & 18.1 ± 27.4 &  & 0.04 ± 6.99 & 0.09 ± 1.84\\
$View_{neg}$ & 187.8 ± 87.3 & 49.4 ± 62.3 &  & 1.03 ± 7.21 & 0.58 ± 3.2\\
Distraction & 158.1 ± 92.5 & 208.5 ± 96.1 & 216.6 ± 93.2 & 0 ± 7.67 & -0.05 ± 1.16\\
Distancing & 164 ± 87.2 & 189.8 ± 92.3 & 214.8 ± 78.6 & 0.25 ± 1.92 & 0.01 ± 1\\
Suppression & 168.6 ± 95.8 & 158.3 ± 99.5 & 229.3 ± 95 & 0.07 ± 3.78 & -0.03 ± 0.92\\
\bottomrule
\end{longtable}

\end{lltable}

@@

We exploratorily wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
The starting point for this was the model reported before.
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification:
\[
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
\]
As one would expect, the predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = -14.26\), \(p < .001\)), utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant association with SVs.
In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.02\), 95\% CI \([0.00, 0.05]\), \(t(97.97) = 2.04\), \(p = .044\)).
However, the effect size of self-control was negligibly small (\(f^{2}=\) 0.002).
Detailed information can be found in the \protect\hyperlink{SupplementExploratory}{supplementary material}.

>>>>

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, \emph{Corrugator} and \emph{Levator} activity of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 0.21\)), \emph{Corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 6.16 \times 10^{7}\)), and \emph{Levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 3.22 \times 10^{17}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc tests, please see tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in the \protect\hyperlink{SupplementEffectER}{supplementary material}.

{[}INSERT TABLE 1 HERE{]}

\caption{\label{tab:TabDescr}$M \pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.}

\begin{tabular}{lccccl}
\toprule
 & \multicolumn{1}{c}{Subjective Arousal} & \multicolumn{1}{c}{Subjective Effort} & \multicolumn{1}{c}{Subjective Utility} & \multicolumn{1}{c}{Corrugator activity (in mV)} & \multicolumn{1}{c}{Levator activity (in mV)}\\
\midrule
$View_{neu}$ & 26.6 ± 39.1 & 18.1 ± 27.4 &  & 0.04 ± 6.99 & 0.09 ± 1.84\\
$View_{neg}$ & 187.8 ± 87.3 & 49.4 ± 62.3 &  & 1.03 ± 7.21 & 0.58 ± 3.2\\
Distraction & 158.1 ± 92.5 & 208.5 ± 96.1 & 216.6 ± 93.2 & 0 ± 7.67 & -0.05 ± 1.16\\
Distancing & 164 ± 87.2 & 189.8 ± 92.3 & 214.8 ± 78.6 & 0.25 ± 1.92 & 0.01 ± 1\\
Suppression & 168.6 ± 95.8 & 158.3 ± 99.5 & 229.3 ± 95 & 0.07 ± 3.78 & -0.03 ± 0.92\\
\bottomrule
\end{tabular}

@@

We exploratorily wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
The starting point for this was the model reported before.
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification:
\[
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
\]
As one would expect, the predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = -14.26\), \(p < .001\)) showed a negative association with SVs, while utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant positive association with SVs.
In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.02\), 95\% CI \([0.00, 0.05]\), \(t(97.97) = 2.04\), \(p = .044\)).
However, the effect size of self-control was negligibly small (\(f^{2}=\) 0.002).
Detailed information can be found in the \protect\hyperlink{SupplementExploratory}{supplementary material}.

### 2023-03-28 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added blank space
table 1 is the anti hero

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression). 
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc tests, please see tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
[INSERT TABLE 1 HERE]

``` {r TabDescr, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  df.descr,
  caption = "$M \\pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.",
  escape = FALSE,
  placement = "H",
  landscape = TRUE)
```

>>>>

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression). 
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc tests, please see tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).

[INSERT TABLE 1 HERE]

``` {r TabDescr, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  df.descr,
  caption = "$M \\pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.",
  escape = FALSE,
  placement = "H",
  font_size = "footnotesize",
  align = c("l","c","c","c","c"))
```
